### 2015-01-18 src/related.Rnw
update intro
updates from amin
update related

\section{Related Work}
\label{sec:related}
There are several approaches to reducing the cost of mutation analysis.
These were categorized by Offutt and Untch~\cite{offutt2001mutation}
into three approaches: do \textit{fewer}, \textit{smarter}, and \textit{faster}.
The \textit{do fewer} approaches include selective mutation and mutant sampling,
while weak mutation, parallelization of mutation analysis, and space/time trade-offs
are grouped under the umbrella of \textit{do smarter}. Finally
\textit{do faster} approaches include mutant schema generation methods,
code patching etc.

>>>>

\section{Related Work}
\label{sec:related}

The idea of mutation analysis was first proposed by Richard Lipton~\cite{mathur2012foundations},
and formalized by DeMillo et al.~\cite{demillo1978hints} A practical implementation of
mutation analysis was accomplished by Budd et al.~\cite{budd1980theoretical} in 1980.

Mutation analysis was found to subsume different coverage measures~\cite{budd1980mutation,mathur1994empirical,offutt1996subsumption},
and it was found that the faults produced by mutation analysis were similar to real
faults in the errors it produced~\cite{daran1996software} and the ease of detection~\cite{andrews2005mutation,andrews2006using}.
Just et al.~\cite{just2014mutants} investigated the relation between mutation score and test
case effectiveness using 357 real bugs, and found that the mutation score increased
with effectiveness for 75\% of the cases, which was better than the 46\% reported
for structural coverage.

The foundational assumptions of mutation analysis are the competent programmer
hypothesis which states that programmers tend to make very simple mistakes, and
coupling effect which states that a test case able to detect a fault in
isolation will continue to detect it even in the presence of other
faults~\cite{demillo1978hints}. This was confirmed using theoretical analysis by Wah~\cite{wah2000atheoretical,wah2003ananalysis}
and using empirical studies by Offutt~\cite{offutt1989thecoupling,offutt1992investigations}

There are several approaches to reducing the cost of mutation analysis.
These were categorized by Offutt and Untch~\cite{offutt2001mutation}
into three approaches: do \textit{fewer}, \textit{smarter}, and \textit{faster}.
The \textit{do fewer} approaches include selective mutation and mutant sampling,
while weak mutation, parallelization of mutation analysis, and space/time trade-offs
are grouped under the umbrella of \textit{do smarter}. Finally
\textit{do faster} approaches include mutant schema generation methods,
code patching etc.
